AERE @ WEAI\\ Rawls for Environmental Justice

### 2025-06-03 weai.tex

\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage{latexsym,amsmath,xcolor,multicol,booktabs,calligra, animate, subfig}
\usepackage{graphicx,pstricks,listings,stackengine, bbm}
\usepackage{tikz}
\usetikzlibrary{fit,tikzmark}   
\usepackage{booktabs,cellspace}
\usepackage{color, colortbl}
\usepackage{hyperref}
\usepackage{color}
%Information to be included in the title page:
\title{Air Pollution from Electricity Production}
\author{Lauren Beatty\\ \href{mailto:lbeatty@edf.org}{lbeatty@edf.org}}
\institute{Environmental Defense Fund}
\date{\today}

@@

\begin{frame}
\frametitle{Introduction}
Two Different Questions / Approaches:
\begin{enumerate}
    \item Downscaling
    \begin{itemize}
        \item \textbf{Question}: How might a particular plan for decarbonization affect air pollution.
        \item \textbf{Method}: Sequentially run a least-cost planning model, then take the outputs of that model and predict pollution.
    \end{itemize}
    \item Endogenous
    \begin{itemize}
        \item \textbf{Question}: What decarbonization plan most dramatically decreases air pollution equitably?
        \item \textbf{Method}: Alter the planning model to minimize pollution subject to a cost constraint.
    \end{itemize}
\end{enumerate}
\vspace{1cm}

\begin{frame}{Background on Least-Cost Electricity Planning Models}
\begin{center}
\begin{tikzpicture}[node distance=2cm]
\node (start) [start, text width=5cm] {\shortstack[l]{Inputs\\• Electricity Demand \\ • Costs of New Generation \\ • Generation Characteristics\\
• Constraints}};

@@

\begin{frame}{Background on Least-Cost Electricity Planning Models: Pros and Cons}
    \begin{itemize}
        \item Powerful for out-of-sample questions

        \item Persuasive in policy arguments.

        \item No or very little backwards validation -- We have no evidence that these models make good predictions about what will happen.

        \item Rely on strong assumptions about future costs and demand, as well as the strong assumption that these are known ex-ante.
    \end{itemize}
\end{frame}

\begin{frame}{Air Pollution Modelling}
\textbf{Translate emissions at points to concentrations over space.}

\vspace{.3cm}

Multiple models of varying complexity. The main models used in policy work are:
\begin{itemize}
    \item APEEP
    \item INMAP
    \item EASIUR
\end{itemize}

\vspace{.3cm}

These are all \textbf{average-annual models}, with reduced-form representations of more complex chemical transport models. Each answers the question: \textit{How much does pollution affect average annual exposure?} Therefore, they are suitable for thinking about policies affecting aggregate emissions, but not suitable for thinking about things like hourly NAAQs.
\end{frame}

\begin{frame}{Downscaling}
\begin{enumerate}
    \item Run least-cost planning model
    \item Model outputs annual generation for each ``resource," such as Combined Cycle Plants in New England ISO North.
    \begin{itemize}
        \item How much resources are aggregated is a user choice which needs to balance computational feasibility and model accuracy.
    \end{itemize}
    \item Translate model outputs into point source locations and aggregate emissions of important pollutants (in InMAP -- PM2.5, NOx, SOx, VOCs, NH3).
        \begin{itemize}
            \item Involves lots of assumptions about how to allocate generation to existing plants, and the location of new plants.
        \end{itemize}
    \item Run those aggregate emissions through an air pollution model of your choice.
    \item Translate concentrations into health impacts.
\end{enumerate}
\end{frame}

\begin{frame}{MIP Results}
    \begin{columns} % Create two columns
        \column{0.5\textwidth} % First column: 50% of slide width
        \centering
        \includegraphics[width=\linewidth]{Figures/Output/full-base-200/GenX/ISRM_2027_TotalPM25_concentrationmap.jpg}
        \captionof{figure}{PM2.5 Concentrations in 2027 in the base-200 scenario}

        \column{0.5\textwidth} % Second column: 50% of slide width
        \centering
        \includegraphics[width=\linewidth]{Figures/Output/full-base-200/GenX/ISRM_2050_TotalPM25_concentrationmap.jpg}
        \captionof{figure}{PM2.5 Concentrations in 2050 in the base-200 scenario}
    \end{columns}
\end{frame}

\begin{frame}{MIP Results}
    \includegraphics[width=\textwidth]{Figures/Output/Compare_scenarios_current-base_GenX.jpg}
\end{frame}

@@

\begin{frame}{Flavor of Results}
    \centering
    \includegraphics[width=0.8\textwidth]{Figures/EndogenousResults/current_policies_short_simplified/exposure_cost_PPF.png}
\end{frame}

@@

    Please feel free to contact me at:
    \href{mailto:lbeatty@edf.org}{lbeatty@edf.org}\\
    \vspace{1cm}
\end{frame}
\end{document}

>>>>

\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage{latexsym,amsmath,xcolor,multicol,booktabs,calligra, animate, subfig}
\usepackage{graphicx,pstricks,listings,stackengine, bbm}
\usepackage{tikz}
\usetikzlibrary{fit,tikzmark}   
\usepackage{booktabs,cellspace}
\usepackage{color, colortbl}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage{color}
\usepackage{changepage} % in your preamble

%Information to be included in the title page:
\title{AERE @ WEAI\\
Rawls for Environmental Justice}
\author{Lauren Beatty\\ \href{mailto:lbeatty@edf.org}{lbeatty@edf.org} \\
\vspace{.3cm}
Matthias Fripp\\
\href{mailto:matthias@energyinnovation.org}{matthias@energyinnovation.org}}
\institute{Environmental Defense Fund}
\date{June 21, 2024}

@@

\section{Introduction}

\begin{frame}{Introduction}
\begin{itemize}
    \item Air pollution is responsible for $\sim 7$ million deaths annually (\href{https://www.who.int/health-topics/air-pollution#tab=tab_2}{WHO}).
    \item In the U.S.,  Black and non-Hispanic white people are exposed to higher levels of air pollution than other groups. Low income people are exposed to higher pollution levels than high income people, controlling for race \citep{Thind2019FineGeography}.
    \item \citet{Lelieveld2015TheScale} estimate that power generation is linked with 31$\%$ of premature mortality caused by outdoor air pollution in the U.S.
\end{itemize}

    \textbf{How can we reduce air quality \textit{equitably?}}
\end{frame}

\begin{frame}{Previous Work}
\begin{itemize}
    \item \citet{Sergi2020OptimizingBenefits} include co-benefits involved with reducing electricity generation from fossil fuels in the objective function.
    \item citep{Goforth2022AirStrategies} and \citep{Shawhan2024PoliciesAmericans} project how the electricity transmission might affect the distributional consequences of air pollution exposure.
\end{itemize}
\end{frame}

\begin{frame}{Least-Cost Electricity Planning Models}
\begin{center}
\begin{tikzpicture}[node distance=2cm]
\node (start) [start, text width=5cm] {\shortstack[l]{Inputs\\• Electricity Demand \\ • Costs of New Generation \\ • Generation Characteristics\\
• Constraints}};

@@

@@

\begin{frame}{Data}

\begin{frame}{Results}
    \begin{itemize}
        \item Imperfect correlation between emissions rates, and effects on pollution.
        \item Modest budgets can dramatically reduce air pollution exposure from electricity generation.
        \item Air quality improvements exhibit decreasing marginal returns.
        \item The mechanisms for reducing air pollution are:
        \begin{itemize}
            \item Expanding wind and solar
            \item Decreasing coal generation faster
            \item Changing the spatial distribution of remaining fossil generation
            \item Increases in transmission
        \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Imperfect Correlation Between Emissions Rates and Effects on Pollution}
\includegraphics[width=0.49\textwidth]{Figures/EndogenousPaper/emissions_by_technology.png}
\includegraphics[width=0.49\textwidth]{Figures/EndogenousPaper/exposure_by_technology.png}
\end{frame}

\begin{frame}{Large Improvements in Air Quality at Modest Costs}
    \centering
    \includegraphics[width=0.8\textwidth]{Figures/EndogenousPaper/exposure_by_scenario_2050.png}
\end{frame}

\begin{frame}{Decreasing Marginal Returns}
    \centering
    \includegraphics[width=0.8\textwidth]{Figures/EndogenousPaper/exposure_cost_PPF.png}
\end{frame}

\begin{frame}{Decreasing Fossil and Increasing Renewable Generation}
\begin{adjustwidth}{-3em}{-1.5em}

    \centering
    \begin{minipage}{1.1\textwidth}
        \centering
        \includegraphics[width=0.32\textwidth]{Figures/EndogenousPaper/Dispatch_Relative_by_scenario_2027.png} \hfill
        \includegraphics[width=0.32\textwidth]{Figures/EndogenousPaper/Dispatch_Relative_by_scenario_2030.png} \hfill
        \includegraphics[width=0.32\textwidth]{Figures/EndogenousPaper/Dispatch_Relative_by_scenario_2035.png}
    \end{minipage}

    \vspace{0.5cm}

    \begin{minipage}{1.1\textwidth}
        \centering
        \includegraphics[width=0.32\textwidth]{Figures/EndogenousPaper/Dispatch_Relative_by_scenario_2040.png} \hfill
        \includegraphics[width=0.32\textwidth]{Figures/EndogenousPaper/Dispatch_Relative_by_scenario_2045.png} \hfill
        \includegraphics[width=0.32\textwidth]{Figures/EndogenousPaper/Dispatch_Relative_by_scenario_2050.png}
    \end{minipage}
\end{adjustwidth}
\end{frame}

\begin{frame}{Increasing Renewable Generation}
    \centering
    \includegraphics[width=0.8\textwidth]{Figures/EndogenousPaper/solar_generation_map.png}
\end{frame}

\begin{frame}{Increasing Renewable Generation}
    \centering
    \includegraphics[width=0.8\textwidth]{Figures/EndogenousPaper/wind_generation_map.png}
\end{frame}

\begin{frame}{Decreasing Coal Faster}
    \centering
    \includegraphics[width=0.8\textwidth]{Figures/EndogenousPaper/coal_generation_map_2027_200B.png}
\end{frame}

\begin{frame}{Changing the Spatial Distribution of Remaining Fossil Generation}
\centering
\includegraphics[width=0.8\textwidth]{Figures/EndogenousPaper/naturalgas_generation_map.png}
\end{frame}
\begin{frame}{Transmission/Capacity Substitution}
    \centering
    \includegraphics[width=\textwidth]{Figures/EndogenousPaper/transmission_capacity_substitution.png}
\end{frame}

@@

    Please feel free to contact me at:
    \href{mailto:lbeatty@edf.org}{lbeatty@edf.org}\\
    \vspace{1cm}
\end{frame}

\begin{frame}{References}
\newpage
\bibliographystyle{jpe}
%\bibliographystyle{econometrica}
\bibliography{references.bib}
\end{frame}
\end{document}
